### 2022-02-07 manuscript.rmd
Move extensions and LOO to `extension.rmd`

abstract: |
  Comparative approaches such as comparative content analysis are frequently used in journalism studies. The purpose of this paper is to argue that researchers should refrain from using current (frequentist) analytical approaches to analyze data from a comparative study. It is because current approaches cannot account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of the data. Bayesian multilevel regression is suggested to be a ---and probably, the only--- valid analytical approach. Using the openly available *useNews* data and the R package *brms*, we demonstrate how to apply the Bayesian approach for the analysis of comparative data. We also address common queries of the approach such as choosing the priors and diagnosing the convergence of the model. Furthermore, we argue that choosing a Bayesian approach also solves the problem of often misinterpreted frequentist confidence intervals.

@@

Although some comparative studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) and their countries (e.g. post-communist country) influence the content of news articles or behaviours of journalists. For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the  degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g. newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g. degree of opinion-orientation), namely, the article-level or journalist-level.

This study of ecological effects on individual behaviors has a long tradition in social sciences. A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide]. Durkheim found the higher suicide rate among citizens from Scandinavian countries than those from other European countries. Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative research. An example of hypothesis-generating comparative research is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative study, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions of the statistical analyses. It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in a multilevel structure. A news article is nested within its media outlet and its media outlet is in turn nested within its country [^author]. Such data structure brings two problems: non-atomicity and non-stochasticity.

[^author]: Theoretically with a large enough data it can be argued that a news article is nested within authors.

In our paper we first discuss these two issues before we suggest Bayesian multilevel regression as a standard approach for comparative research in journalism studies. While Bayesian models might be slightly more complicated to estimate in contrast to frequentist models as priors have to be chosen, these models allow researchers to make "principled statements about precision and plausibility" [@morey:2015 p. 121] and solve the issue of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA]. Using the openly available *useNews* and WJS datasets and the R package *brms*, we then demonstrate how to apply a Bayesian approach for the analysis of comparative data.

@@

It is perhaps well-known what ecological fallacy is. We commit ecological fallacy, when we make inference at micro-level (e.g. Eating more chocolate makes one cleverer) based on macro-level data (e.g. the correlation between countries' chocolate consumption and countries' number of Nobel winners). The reverse of ecological fallacy, i.e. making inference at macro-level based on micro-level data, is equally fallacious. This fallacy is called atomistic fallacy [@gnaldi:2018:EFC].

@@

This method is the so-called "disaggregation approach". From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to atomistic fallacy [@hox2017multilevel]. From a statistical standpoint, this approach violates the underlying independence assumption. Almost all frequentist statistical tests assume that the observations are independent of each other: $y_{i}$ given $x_{i}$ are independently identically distributed (i.i.d.). Articles from the same media outlet are hardly i.i.d.: they are subjected to being edited by the same editorial team, to being written by the same group of journalists exposed to the same journalistic culture and paid for by the same employer. Also, the way communication researchers collect their media content resembles cluster sampling rather than random sampling: one usually starts from a specific media outlet and then collects all relevant articles from it. The choice of media outlets or countries are almost always not randomly selected. [^1] This sampling approach makes the independence assumption even more fragile.

@@

Comparative content analytic studies in journalism studies, unlike randomized surveys or randomized media experiments, often collect all available data. In contrast to sampling, these studies are actually doing census of all data. There is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA]. It is especially true for modern large-N studies using automated content analytic techniques. @burggraaff:2017:T, for instance, "collected all available news items from a selection of major Dutch news outlets, both online and print" (p. 6) and that amounted to 762,095 articles from 9 outlets in the period of 2014--2015.

@@

Before we move on to the next section, it is important to point that **non-stochastic data is not an essential condition for applying the Bayiesan approach**. The same approach is equally applicable to both non-stochastic and stochastic comparative datasets. Therefore, one can analyse both randomized comparative surveys (such as WJS) and comparative content analytic studies with the same Bayesian analytic approach.

@@

What is the probability for this paper being accepted by *Digital Journalism*? Under the frequentist framework (and if *Digital Journalism* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *Digital Journalism*, say for 100 times, and then count the frequency of acceptance in these repeated submissions. It is indeed impractical as well as inhumane to the editorial team of *Digital Journalism*. Instead, we assert before submission that this paper has a probability of 24% for being accepted. That is the published acceptance rate from *Digital Journalism*’s website. After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%. After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%. After the paper is favorably reviewed by two reviewers and an R&R is invited, the probability might increase to 40% to 60%. If you see this paper under the "Latest articles" section of *Digital Journalism*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).

@@

The $P(X| \theta)$ part is called likelihood function. In the *Digital Journalism* example, the likelihood function is based on rough rules from our experience and thus is not systematic [^dj]. In actual analysis, we need to derive such a likelihood function based on the available data using methods such as Markov Chain Monte Carlo (MCMC). Nonetheless, the above equation indicates that there are only three ingredients in any Bayesian analysis: 1) data ($X$), 2) a method to derive the likelihood function $P(X | \theta)$ from the data, and 3) prior, $P(\theta)$.

[^dj]: As a side note: we have actually performed the experiment by submitting this paper to *Digital Journalism*. But for pragmatic reasons we cannot report the posterior.

@@

Part 3 (Prior) is arguably the most controversial part of Bayesian analysis. In the *Digital Journalism* example, we can select a reasonable prior (or **informative** prior) of 24% from published information. Finding previous studies for an informative prior is the logical first thing to do. @keating:2019:W show that one in every seven communication research papers published in major communication journals was a form of replication attempt. For these one seventh of communication research, there should be previous studies available to base one’s informative prior non-controversially.

@@

But one person's expert opinion could be another person's wishful thinking. And this perceived subjectivity of specifying priors by experts’ judgement attracts wide-spread criticism from both statisticians [e.g. @efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].

@@

Bayesian analysis is still a minority statistical method in social sciences. It is reasonable to say that Bayesian analysis is extremely rare in our field. Although some communication researchers adopted the method [e.g. @kovic:2017:B;@chan2020high] these studies are not comparative. As far as we know, the only available comparative research in journalism studies that Bayesian multilevel regression was used for studying ecological effect is @leeuw:2020:AAT. We believe comparative communication research fits the use case of Bayesian multilevel regression analysis. Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of this paper is to demonstrate how to actually do the analysis using the R package *brms* [@burkner2017advanced]. As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar. The above quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.

The two examples below show how the Bayesian multilevel regression analysis can be deployed to the common archtypes of comparative journalism studies. The first example is an analysis of a comparative, non-stochastic content analytic dataset. The second example is an analysis of a comparative, stochastic survey dataset.

@@

The useNews is an openly available dataset [@puschmann:2020] that includes 2019 to 2020 media content data from an array of worldwide media outlets . The media content data was collected from the MIT MediaCloud and made available as document-term matrices.

@@

[^dict_val]: One might argue our seed dictionaries are not validated. We deem that the criterion validity of our dictionary should be built-in. Coverage of China, by definition, should mention words about China. We also maintain that it is difficult to conduct a human validation of the seed dictionaries because the useNews dataset [@puschmann:2020] doesn’t provide access to the full-length articles. Nonetheless, we attempted to conduct such validation by randomly selecting 10 matching and 10 non-matching items for each language. In total, 160 items were selected. A coder with no knowledge of the ground truth (matching or not) annotated the full-text articles by following the URLs in the meta data provided in the useNews dataset [@puschmann:2020]. For some languages, the coder used Google Translate to translate the full text article to English. In total, only 138 URLs were still accessible. Comparing the ground truth and the human coding, 62 and 70 are true-positive and true-negative cases. There are also 5 false-negative and 1 false-positive cases. There are several reasons not related to our seed dictionaries that could lead to the 6 misclassified cases. The false-positive case is Korean and that could be due to incorrect tokenization at the MIT Media Cloud’s end. The 5 false-negative cases are in Norwegian, Portuguese, and Romanian. The content on the website might have changed since MIT Media Cloud collected the data. For example, the ever-changing content in the sidebar might be counted as “main content” and recorded in the DTM. Despite all these caveats, our seed dictionaries have a precision and recall of 98.4% and 92.5% respectively. For the purpose of demonstrating regression analysis, this level of accuracy is more than sufficient.

@@

We used logistic regression for this analysis. Due to the computational time needed to conduct the Bayesian regression in this case (it took 4 days on a regular computer), we only did the model with import volume as the independent variable.

@@

Other parameters for Bayesian multilevel regression analysis control how the MCMC should be performed. Three parameters are important: number of iterations, number of chains and *adapt_delta*. They are not some magic numbers that you can plug and play. However, it is in general safe to use the default values, i.e. number of iterations = 2000, number of chains = 4 and *adapt_delta* = 0.8, unless MCMC shows evidence of nonconvergence. *brms* is smart enough to give suggestions on how to adjust these three values. Nonetheless, we provide a short guide on how to diagnose convergence.

@@

[^5]: HDI is one representation of the Bayesian credible interval. It is important to note that, like confidence intervals, there should be no "correct" choice of the level of credibility but some established conventions. We choose, like many published works [e.g. @stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\% to maintain "compatibility" with the established convention of reporting 95\% confidence interval. However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing]. Some Bayesians, notably, Andrew Gelman, report very liberal 50\% credible intervals. @mcelreath2020statistical selects 89\% to show the arbitrariness of the practice. @leeuw:2020:AAT select 90\%.

@@

Increasing the number of iterations did change a bit of the estimates, but only at the second decimal place. It shows that the results are consistent between two analyses.

@@

```{r fig3, echo = FALSE, fig.cap = "Posterior predictive checks with 100 sets of simulated data"}
pp_check(import_brms, nsamples = 100)
```

## Extentions

We propose several extensions to the above barebone analysis. The analyses in these extensions are not preregistered.

### Extension #1: Hypothesis testing

Under the Bayesian framework, we can test hypotheses about the parameter estimates [@shikano:2019:HTB]. These hypotheses are similar to the null hypothesis in the Neyman-Pearson's sense. For example, we want to test the two-sided hypothesis of $\gamma_{01} = 0$ for Model A1. For this, we need to calculate the posterior probability of this hypothesis: $P(\gamma_{01} = 0 | X)$. The function *hypothesis()* can be used to test such hypothesis.

```r
hypothesis(import_brms, "logx_import = 0")
```

The posterior probability of this hypothesis is 0. Therefore, we can safely reject the hypothesis and conclude that $\gamma_{01} \neq 0$, i.e. log import volume of the outlet's country is associated with the frequency of China coverage at the outlet level.

While accepting a null hypothesis is not a feasible option in a frequentist framework, as such a framework has an "inability to gain evidence for the null" [@rouder:2009:B, p. 226] hypothesis, it is practically possible to  accept a null hypothesis in a Bayesian framework [@kruschke:2018:RAP]. Bayes factor or the region of practical equivalence (ROPE) could be used to decide to accept the null hypothesis. @kruschke:2018:RAP, for example, suggests using $\sigma = \pm 0.1$ as half of small effect size to establish a ROPE. However, there is no fixed rule on how to define a ROPE. If now 95\% of the HDI for an estimate falls within the ROPE, researchers could accept the null hypothesis for practical purposes. A practical application could be with manual content analysis or survey research in communication research if some variables are challenging and costly to measure. In a frequentist framework, failing to reject the null hypothesis could wrongly inform researchers to collect more data in subsequent studies to discern between insufficient power [^POWER] or the null is true. Instead, ROPE could be used to decide whether, in future studies, more data should be collected to retest the same hypothesis. When ROPE provides a strong signal that the null hypothesis is true, it is no longer worthy to collect more of the costly data just to boost the statistical power.

[^POWER]: Statistical power is a frequentist concept specifying the long run probability of correctly rejecting the null hypothesis. It is usually not relevant for Bayesian inference.

The package bayestestR [@makowski:2019] can be used to calculate and visualize the ROPE.

```r
library(bayestestR)
rope(import_brms)
plot(rope(import_brms))
```

```{r, include = FALSE}
library(bayestestR)
fig <- plot(rope(import_brms))
```

```{r figrope, results = "asis", fig.cap = "The Region of Practical Equivalence and the 95% High Density Interval"}
fig
```

The proportion of 95\% HDI falling inside the ROPE is 0\%. Figure \@ref(fig:figrope) also displays that the 95\% HDI (the pink region) have no overlap with the ROPE (the shaded region). Using the decision rules by @kruschke:2018:RAP, there are 3 possible scenarios: reject the null (when most of the 95\% HDI falls outside the ROPE), accept the null (when most of the 95\% HDI falls inside the ROPE) and undecided (when it can’t be decided). In the current situation, it is very clear that the 95\% HDI falls outside of the ROPE as there is 0\% overlap. Similar to the result from *hypothesis()*, there is a practical effect and it is correct to reject the null hypothesis.

However, in another situation when we have a simulated independent variable *noise* that is basically random noise.

```r
outlet_data$noise <- rnorm(nrow(outlet_data))

noise_brms <- brm(z~offset(log(n))+(1|k)+noise,
                  data = outlet_data, family = negbinomial(),
                  control = list(adapt_delta = 0.99),
                  prior = weaklyinformative_prior,
                  sample_prior = TRUE)
rope(noise_brms)
```

In this situation, the proportion of 95\% HDI falls inside the ROPE is 68\%. The proportion is quite high but it is not decisive. @kruschke:2018:RAP suggests accepting the null when more than 95\% of the 95\% HDI falls inside the ROPE. Accordingly, the current situation of 68\% is "undecided". It might be worthwhile to retest the hypothesis with a larger amount of data.

One should note that the decision rules by @kruschke:2018:RAP depend on many methodological decisions, e.g. how to determine the ROPE, how wide should the ROPE be, and which level of HDI to use. ROPE is also sensitive to the scale of measurement. Nonetheless, ROPE can provide much richer information to inform how future studies should be designed.

### Extension #2: Cross-level interaction

We can also study the interaction between a macro- and a micro-level variable. Cross-level interaction is useful to study how the effect of context variables manifest differently in individuals with different characteristics. An example of cross-level interaction in our example is whether the relationship between import volume and increase in China coverage manifests differently between public broadcasters and for-profit media.

We can model a cross-level interaction by adding an interaction term between the macro- and micro-level variables, as well as a varying-slope component for the micro-level variable [@heisig:2019:WYS]. With *brms*, it can be done with this:

```r
# suppose "public" is a binary variable
import_brms_public <- brm(
      z~offset(log(n))+(1 + public|k)+log(x_import)*public,
      data = outlet_data, family = negbinomial(),
      prior = weaklyinformative_prior, sample_prior = TRUE)
import_brms_public
```

The regression coefficients for the main effect of public broadcasting and the interaction terms have a wide 95\% HDI that covers zero. It can be visualized with a conditional effects plot (Figure \@ref(fig:fig4), using the *conditional_effects()* function). The trajectories of public broadcasters and for-profit media outlets are similar, indicating no interaction.

```{r fig4, echo = FALSE, fig.cap = "Conditional effects plot showing no interaction among public broadcasting, import volume and China coverage."}
require(ggplot2)
condit_plots <- readRDS("condit_plots.RDS")
condit_plots$`x_import:public` + xlab("Import Volume") + ylab("Number of articles mentioning China per 10,000 articles") + scale_x_continuous(labels = scales::comma) + theme_minimal() + scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2")
```

### Extension #3: Current study as the informative prior for the next study

Suppose we would like to replicate the study and confirm the same relationship with the 2020 useNews data. This time, we do not need to (and actually, we should not) use the weakly informative prior again. It is because we have *prior* understanding about the outlet-level determinants of China coverage: We know from the 2019 data that $\gamma_{01}$ should be around 0.25 with a standard deviation of 0.05. This can be entered into our new analysis as the informative prior.

```r
informative_prior <- c(prior_string("normal(0.25, 0.05)", class = "b",
                                    coef = "logx_import"),
                       prior_string("normal(-6.69, 0.66)",
                                    class = "Intercept"))
import_2020 <- brm(z_2020~offset(log(n_2020))+(1|k)+log(x_import),
                   data = outlet_data2020, family = negbinomial(),
                   prior = informative_prior, sample_prior = TRUE)
```

The new analysis showed that $\gamma_{01}$ is 0.22 with a 95\% HDI of (0.15 to 0.29) for the year 2020. This analysis displays two things: 1) selection of prior is not always, as many authors have suggested, as controversial and subjective; and 2) Bayesian analysis also makes a strong case for replication studies, which open science hopes to enable [@dienlin:2020:AOS]. The use of informative prior in replication studies enables us to update our prior beliefs with the new evidence from the replications. Priors, replicable or not, will get updated.

## Extension #4: Temporal changes

Bayesian multilevel regression analysis is also useful to study temporal changes, because observations from the same subject collected from different time points are naturally a cluster. The same strategy for handling the clustering of observations in the multilevel modeling can be used. We model that observations from the same media outlet are nested within the media outlet and then the media outlet is nested within its countries. Suppose we would like to study if there is a systematic increase in $z$ across all outlets, maybe due to the COVID-19 pandemic or the presidential election in the US. It can be analyzed with this three-level model.

```r
## Suppose yr is a binary dummy variable indicating the year 2020.
import_long <- brm(z~offset(log(n))+(1|k/i)+yr, data = outlet_long,
                   family = negbinomial(),
                   prior = weaklyinformative_prior,
                   sample_prior = TRUE)
import_long
```

The regression coefficient for the year dummy variable is 0.49 (95\% HDI 0.38, 0.60). There is a global increase in China coverage from 2019 to 2020.

@@

Example 1 above demonstrated how to conduct a Bayesian multilevel regression analysis. In this example, the same approach is applied to a stochastic dataset from a randomize survey. The starting point of this example is the recent study by @hamada:2021:DJA. Using the second wave data from WJS (2012-2016), the study seeks to study this hypothesis (the H2a in the paper): *The greater the level of democracy in a country, the more perceived professional autonomy journalists enjoy*.

It is important to point out that the study is actually a replication. The same hypothesis has been studied in an earlier study by @reich:2013:DJP, which uses the first wave data from WJS and has a remarkable similar title to that of @hamada:2021:DJA. The earlier study has studied this hypothesis (the H4): *Journalists’ perceived professional autonomy is positively associated with democratic performance and press freedom, and it is negatively related to political parallelism and state intervention.* The operationalizations of both professional autonomy (based on two questions in WJS) and level of democracy (based on the Economist Intelligence Unit's Index of Democracy) are the same in the two studies.

@@

There are two weaknesses of the aggregated approach. First, a massive amount of information at the author-level was discarded and cannot leverage the hierarchical structure of the data. As showed in @reich:2013:DJP, author-level variables such as year of experience and being in a management position are also predictive of perceived professional autonomy. Taking the aggregated approach assumes that all of these author-level variables are homogeneous. This assumption could create spurious correlation when the distribution of author-level variables is associated with contextual factors, e.g. Index of Democracy. Second, the two hypotheses specified in the two quoted studies refer to the perception at the micro-level ("the more perceived professional autonomy journalists enjoy", "Journalists’ perceived professional autonomy"), not at the macro-level (e.g. the average level of perceived professional autonomy of journalists in a country). Interpreting the macro-level association wrongly at the micro-level leads to ecological fallacy.

@@

Let's assume we were in the shoes of @hamada:2021:DJA and wanted to replicate the study by @reich:2013:DJP with the second wave WJS data. Bayesian multilevel regression is probably the only valid approach. First, it can take advantage of the hierarchical structure of the data and correctly estimate the contextual effect of democracy performance at the journalist-level perceived professional autonomy. Second, the incorporating of prior information from @reich:2013:DJP makes the intention to replication clearer.

@@

The following is the complete code to construct the two Bayesian model. The cubic relationship can be set using the `I()` function.

@@

By looking at the regression coefficient and the 95\% HDI, the standardized regression coefficient for Index of Democracy is 0.24 (95\% HDI: 0.13 to 0.34). It is not only statistical significant in the traditional sense but also the strongest predictor among all other predictors (Rank: 0.15, Experience: 0.08, gender: -0.06, university degree: -0.01). It supports @hamada:2021:DJA's h2a, but our model does that without the problem of aforementioned ecological fallacy and with adjustment for other potential confounders.

>>>>

abstract: |
  Comparative approaches such as comparative content analysis are frequently used in journalism studies. The purpose of this paper is to argue that researchers should refrain from using current (frequentist) analytical approaches to analyze data from a comparative study. It is because current approaches cannot account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of the data. Bayesian multilevel regression is suggested to be a ---and probably, the only--- valid analytical approach. Using the openly available *useNews* and *Worlds of Journalism Study* datasets and the R package *brms*, we demonstrate how to apply the Bayesian approach for the analysis of comparative data. We also address common queries of the approach such as choosing the priors and diagnosing the convergence of the model. Furthermore, we argue that choosing a Bayesian approach also solves the problem of often misinterpreted frequentist confidence intervals.

@@

Although some comparative studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) and their countries (e.g. post-communist country) influence the content of news articles or behaviours of journalists. For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the  degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g., newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g., degree of opinion-orientation), namely, the article-level or journalist-level.

This study of ecological effects on individual behaviors has a long tradition in social sciences. A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide]. Durkheim found a higher suicide rate among citizens from Scandinavian countries than those from other European countries. Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative research. An example of hypothesis-generating comparative research is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative study, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions of the statistical analyses. It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in a multilevel structure. A news article is nested within its media outlet and its media outlet is in turn nested within its country [^author]. Such data structure brings two problems: non-atomicity and non-stochasticity.

[^author]: Theoretically, with large enough data it can be argued that a news article is nested within authors.

In our paper, we first discuss these two issues before we suggest Bayesian multilevel regression as a standard approach for comparative research in journalism studies. While Bayesian models might be slightly more complicated to estimate in contrast to frequentist models as priors have to be chosen, these models allow researchers to make "principled statements about precision and plausibility" [@morey:2015 p. 121] and solve the issue of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA]. Using the openly available *useNews* and WJS datasets and the R package *brms*, we then demonstrate how to apply a Bayesian approach for the analysis of comparative data.

@@

It is perhaps well-known what ecological fallacy is. We commit ecological fallacy, when we make inference at the micro-level (e.g. Eating more chocolate makes one cleverer) based on macro-level data (e.g. the correlation between countries' chocolate consumption and countries' number of Nobel winners). The reverse of ecological fallacy, i.e. making inference at macro-level based on micro-level data, is equally fallacious. This fallacy is called atomistic fallacy [@gnaldi:2018:EFC].

@@

This method is the so-called "disaggregation approach". From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to atomistic fallacy [@hox2017multilevel]. From a statistical standpoint, this approach violates the underlying independence assumption. Almost all frequentist statistical tests assume that the observations are independent of each other: $y_{i}$ given $x_{i}$ are independently identically distributed (i.i.d.). Articles from the same media outlet are hardly i.i.d.: they are subjected to being edited by the same editorial team, to being written by the same group of journalists exposed to the same journalistic culture and paid for by the same employer. Also, the way communication researchers collect their media content resembles cluster sampling rather than random sampling: one usually starts from a specific media outlet and then collects all relevant articles from it. The choice of media outlets or countries is almost always not randomly selected. [^1] This sampling approach makes the independence assumption even more fragile.

@@

Comparative content analytic studies in journalism studies, unlike randomized surveys or randomized media experiments, often collect all available data. In contrast to sampling, these studies are actually doing a census of all data. There is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA]. It is especially true for modern large-N studies using automated content analytic techniques. @burggraaff:2017:T, for instance, "collected all available news items from a selection of major Dutch news outlets, both online and print" (p. 6) and that amounted to 762,095 articles from 9 outlets in the period of 2014--2015.

@@

Before we move on to the next section, it is important to point that **non-stochastic data is not an essential condition for applying the Bayesian approach**. The same approach is equally applicable to both non-stochastic and stochastic comparative datasets. Therefore, one can analyze both randomized comparative surveys (such as WJS) and comparative content analytic studies with the same Bayesian analytic approach.

@@

What is the probability for this paper being accepted by *Journalism Studies*? Under the frequentist framework (and if *Journalism Studies* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *Journalism Studies*, say for 100 times, and then count the frequency of acceptance in these repeated submissions. It is indeed impractical as well as inhumane to the editorial team of *Journalism Studies*. Instead, we assert before submission that this paper has a probability of 24% for being accepted. That is the published acceptance rate from *Journalism Studies*’s website. After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%. After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%. After the paper is favorably reviewed by two reviewers and an R&R is invited, the probability might increase to 40% to 60%. If you see this paper under the "Latest articles" section of *Journalism Studies*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).

@@

The $P(X| \theta)$ part is called likelihood function. In the *Journalism Studies* example, the likelihood function is based on rough rules from our experience and thus is not systematic. In actual analysis, we need to derive such a likelihood function based on the available data using methods such as Markov Chain Monte Carlo (MCMC). Nonetheless, the above equation indicates that there are only three ingredients in any Bayesian analysis: 1) data ($X$), 2) a method to derive the likelihood function $P(X | \theta)$ from the data, and 3) prior, $P(\theta)$.

@@

Part 3 (Prior) is arguably the most controversial part of Bayesian analysis. In the *Journalism Studies* example, we can select a reasonable prior (or **informative** prior) of 24% from published information. Finding previous studies for an informative prior is the logical first thing to do. @keating:2019:W show that one in every seven communication research papers published in major communication journals was a form of replication attempt. For these one seventh of communication research, there should be previous studies available to base one’s informative prior non-controversially.

@@

But one person's expert opinion could be another person's wishful thinking. And this perceived subjectivity of specifying priors by experts’ judgment attracts wide-spread criticism from both statisticians [e.g. @efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].

@@

Bayesian analysis is still a minority statistical method in social sciences. It is reasonable to say that Bayesian analysis is extremely rare in our field. Although some communication researchers adopted the method [e.g. @kovic:2017:B;@chan2020high], these studies are not comparative. As far as we know, the only available comparative research in journalism studies that Bayesian multilevel regression was used for studying ecological effect are @leeuw:2020:AAT and @heidenreich:2022:DE. We believe comparative communication research fits the use case of Bayesian multilevel regression analysis. Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of the rest of this paper is to demonstrate how to actually do the analysis using the R package *brms* [@burkner2017advanced]. As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar. The above-quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.

The two examples below show how the Bayesian multilevel regression analysis can be deployed to the common archetypes of comparative journalism studies. The first example is an analysis of a comparative, non-stochastic content analytic dataset. The second example is an analysis of a comparative, stochastic survey dataset.

@@

The useNews is an openly available dataset [@puschmann:2020] that includes 2019 to 2020 media content data from an array of worldwide media outlets. The media content data was collected from the MediaCloud and made available as document-term matrices.

@@

[^dict_val]: The validation of the dictionary is available in the Appendix.

@@

We used logistic regression for this analysis. However, due to the computational time needed to conduct the Bayesian regression in this case (it took 4 days on a regular computer), we only did the model with import volume as the independent variable.

@@

Other parameters for Bayesian multilevel regression analysis control how the MCMC should be performed. Three parameters are important: number of iterations, number of chains and *adapt_delta*. They are not some magic numbers that you can plug and play. However, it is in general safe to use the default values, i.e. number of iterations = 2000, number of chains = 4 and *adapt_delta* = 0.8, unless MCMC shows evidence of nonconvergence. *brms* is smart enough to suggest how to adjust these three values. Nonetheless, we provide a short guide on how to diagnose convergence.

@@

[^5]: HDI is one representation of the Bayesian credible interval. It is important to note that, like confidence intervals, there should be no "correct" choice of the level of credibility but some established conventions. We choose, like many published works [e.g. @stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\% to maintain "compatibility" with the established convention of reporting 95\% confidence interval. However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing]. Some Bayesians, notably Andrew Gelman, report very liberal 50\% credible intervals. @mcelreath2020statistical selects 89\% to show the arbitrariness of the practice. @leeuw:2020:AAT select 90\%.

@@

Increasing the number of iterations did change a bit of the estimates, but only at the second decimal place. It shows that the results are consistent between the two analyses.

@@

```{r fig3, echo = FALSE, fig.cap = "Posterior predictive checks with 100 sets of simulated data"}
pp_check(import_brms, ndraws = 100)
```

## Extensions

We propose several extensions to the above barebone analysis: hypothesis testing, investigating cross-level interaction, establishing informative prior, and testing for temporal changes. The analyses in these extensions are not preregistered. Please refer to Appendix I for these extensions.

@@

Example 1 above demonstrated how to conduct a Bayesian multilevel regression analysis. In this example, the same approach is applied to a stochastic dataset from a randomized survey. The starting point of this example is the recent study by @hamada:2021:DJA. Using the second wave data from WJS (2012-2016), the study seeks to study this hypothesis (the H2a in the paper): *The greater the level of democracy in a country, the more perceived professional autonomy journalists enjoy*.

It is important to point out that the study is actually a replication. The same hypothesis has been studied in an earlier study by @reich:2013:DJP, which uses the first wave data from WJS and has a remarkably similar title to that of @hamada:2021:DJA. The earlier study has studied this hypothesis (the H4): *Journalists’ perceived professional autonomy is positively associated with democratic performance and press freedom, and it is negatively related to political parallelism and state intervention.* The operationalizations of both professional autonomy (based on two questions in WJS) and level of democracy (based on the Economist Intelligence Unit's Index of Democracy) are the same in the two studies.

@@

There are two weaknesses of the aggregated approach. First, a massive amount of information at the author-level was discarded and cannot leverage the hierarchical structure of the data. As shown in @reich:2013:DJP, author-level variables such as year of experience and being in a management position are also predictive of perceived professional autonomy. Taking the aggregated approach assumes that all of these author-level variables are homogeneous across countries. This assumption could create spurious correlation when the distribution of author-level variables is associated with contextual factors, e.g. Index of Democracy. Second, the two hypotheses specified in the two quoted studies refer to the perception at the micro-level ("the perceived professional autonomy journalists enjoy", "Journalists’ perceived professional autonomy"), not at the macro-level (e.g. the average level of perceived professional autonomy of journalists in a country). Interpreting the macro-level association wrongly at the micro-level leads to ecological fallacy.

@@

Let's assume we were in the shoes of @hamada:2021:DJA and wanted to replicate the study by @reich:2013:DJP with the second wave WJS data. Bayesian multilevel regression is probably the only valid approach. First, it can take advantage of the hierarchical structure of the data and correctly estimate the contextual effect of democracy performance on the journalist-level perceived professional autonomy. Second, the incorporating of prior information from @reich:2013:DJP makes the intention to replicate clearer.

@@

The following is the complete code to construct the two Bayesian models. The cubic relationship can be set using the `I()` function.

@@

By looking at the regression coefficient and the 95\% HDI, the standardized regression coefficient for Index of Democracy is 0.24 (95\% HDI: 0.13 to 0.34). The Index of Democracy is not only a substantial predictor as 0 is not covered by the 95% HDI but also the strongest predictor among all other predictors (Rank: 0.15, Experience: 0.08, gender: -0.06, university degree: -0.01). It supports @hamada:2021:DJA's h2a, but our model does that without the problem of the aforementioned ecological fallacy and with adjustment for other potential confounders.
